---
title: "Trends of international student admission in NCHU"
author: "Brian"
date: "6/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.align = 'center')
options(tibble.print_max = Inf)
library(xlsx)
library(tidyverse)
library(ggplot2)
library(networkD3)
library(htmlwidgets)
library(treemap)
library(kableExtra)
source("mSankey.R", local = knitr::knit_global())
```

We analyzed data of 'admitted' international students in 2021 to discover trends in higher education in Taiwan. (work in progress)

<!-- #### Import data -->

```{r}
prefix <- "NCHU"
dataset <- read.xlsx("NCHU_2021.xlsx","Sheet1",header=TRUE)
dataset <- dataset %>%
  mutate(College = str_remove(College,"College of ")) %>%
  mutate(Department = str_remove(Department,"Department of "))
```

<!-- Inspect data structure -->

<!-- ```{r} -->
<!-- str(dataset) -->
<!-- ``` -->

**Descriptive statistics**

First of all, descriptive statistics by nationality, college, department, and degree are presented.

By nationality

```{r}
dataset %>%
  count(Nationality, sort=TRUE) %>%
  mutate(Nationality=paste(Nationality,n,sep="\n")) %>%
  treemap(index="Nationality",
      vSize="n", title="Nationality"
  )

knitr::kable(
dataset %>%
  group_by(Nationality) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  mutate( "%" = round(count / sum(count) * 100 ,1))

) %>%
  kable_styling(full_width = F)
```

By college

```{r}
dataset %>%
  count(College, sort=TRUE) %>%
  mutate(College=paste(College,n,sep="\n")) %>%
  treemap(index="College",
      vSize="n", title="College"
  )
knitr::kable(
dataset %>%
  group_by(College) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  mutate( "%" = round(count / sum(count) * 100 ,1))
) %>%
  kable_styling(full_width = F)
```

By department

```{r}
dataset %>%
  count(Department, sort=TRUE) %>%
  mutate(Department=paste(Department,n,sep="\n")) %>%
  treemap(index="Department",
      vSize="n", title="Department"
  )
knitr::kable(
dataset %>%
  group_by(Department) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  mutate( "%" = round(count / sum(count) * 100 ,1))
) %>%
  kable_styling(full_width = F)
```

By degree

```{r}
dataset %>%
  count(Degree, sort=TRUE) %>%
  mutate(Degree=paste(Degree,n,sep="\n")) %>%
  treemap(index="Degree",
      vSize="n", title="Degree"
  )
knitr::kable(
dataset %>%
  group_by(Degree) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  mutate( "%" = round(count / sum(count) * 100 ,1))
) %>%
  kable_styling(full_width = F)
```

**Interrelationship analysis**

The results of multi-variate analysis are presented here.

- Nationality and college
- Nationality and department
- Nationality and degree
- Department and degree
- Degree, nationality, and department
- Degree, nationality, and college

Nationality and college

The height of rectangular indicates the number of students. The width of the line indicates the number of students between connected rectangular

```{r echo=FALSE, message=FALSE}
mSankey(dataset,prefix,"Nationality","College")
```

Nationality and department

```{r echo=FALSE, message=FALSE}
mSankey(dataset,prefix,"Nationality","Department")
```

Nationality and degree

```{r echo=FALSE, message=FALSE}
mSankey(dataset,prefix,"Nationality","Degree")
```

Department and degree

```{r echo=FALSE, message=FALSE}
mSankey(dataset,prefix,"Department","Degree")
```

Degree, nationality, and department

```{r echo=FALSE, message=FALSE}
mSankey(dataset,prefix,"Degree","Nationality","Department")

```

<!-- Nationality, college, and department -->

<!-- ```{r echo=FALSE, message=FALSE} -->
<!-- mSankey(dataset,prefix,"Nationality","College","Department") -->
<!-- ``` -->

Degree, nationality, college

```{r echo=FALSE, message=FALSE}
mSankey(dataset,prefix,"Degree","Nationality","College")
```

Go to [comparison](https://briankimstudio.github.io/New_student/)

```{r child = 'Menu.Rmd'}
```
