---
title: "NCTU"
author: "BK"
date: "6/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, fig.align = 'center')
library(xlsx)
library(tidyverse)
library(ggplot2)
library(networkD3)
library(htmlwidgets)
library(treemap)
library(kableExtra)
source("mSankey.R", local = knitr::knit_global())

sName <- "National Yang Ming Chiao Tung University國立陽明交通大學"
sURL  <- "https://www.nycu.edu.tw"
sCode <- "NCTU"
sYear <- "2020"
fName <- paste0(sCode,"_",sYear,".xlsx")

dataset <- read.xlsx(fName,"Sheet1",header=TRUE)
dataset <- dataset %>% mutate(Department = gsub("[^A-Za-z. &()]","",Department),
                              Degree = gsub("[^A-Za-z. &()]","",Degree))
dataset <- dataset %>% 
  mutate(Department = str_remove(Department,"Department of |Dept. of |Inst. of ")) 

nSize <- dataset %>% count()
```


### What do international students study?(work in progress)

The data of international students admitted to [`r sName`](`r sURL`)(`r sYear`,n=`r nSize`) are analyzed.

By department

```{r}
dataset %>%
  count(Department, sort=TRUE) %>%
  mutate(Department = paste(Department,n,sep="\n")) %>%
  treemap(index="Department",
      vSize="n", title="Department"
  )
knitr::kable(
dataset %>%
  group_by(Department) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  mutate( "%" = round(count / sum(count) * 100 ,1))
) %>%
  kable_styling(full_width = F)
```

By degree

```{r}
dataset %>%
  count(Degree, sort=TRUE) %>%
  mutate(Degree=paste(Degree,n,sep="\n")) %>%
  treemap(index="Degree",
      vSize="n", title="Degree"
  )
knitr::kable(
dataset %>%
  group_by(Degree) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  mutate( "%" = round(count / sum(count) * 100 ,1))
) %>%
  kable_styling(full_width = F)
```

Degree and Department

The height of rectangular indicates the number of students. The width of the line indicates the number of students between connected rectangular.

```{r echo=FALSE, message=FALSE,  fig.align = "center", fig.cap="National Chengchi University"}
mSankey(dataset,prefix,"Degree","Department")
```

```{r child = 'Menu.Rmd'}
```

Note:

1. "Admitted' international student indicates someone who has received an acceptance letter from the university.
2. The accuracy of results would be increased if data of ‘enrolled’ international students are analyzed.