---
title: "International students in Taiwan"
author: "Brian"
date: "6/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(ggplot2)
library(readxl)
library(ggrepel)
library(viridis)
library(kableExtra)
dataset <- read_excel(path = "109_ab108.xlsx",sheet=2,col_names = TRUE)
countries <- read_excel(path="Countries.xlsx", sheet=1,col_names = TRUE)
coordinates <- read_excel(path="Coordinates.xlsx", sheet=1,col_names = TRUE)
data <- dataset %>% left_join(select(countries,Country,Chinese),by=c("Country"="Chinese"))
data <- data %>% select(Country.y,Degree,Exchange,Language)
colnames(data)=c('Country','Degree','Exchange','Language')
data <- data %>% left_join(select(coordinates,Country,latitude,longitude),coordinates,by='Country')

worldmap <-  maps::map("world", fill=TRUE, plot=FALSE) %>%
  maptools::pruneMap(xlim = c(-180,180), ylim = c(-60,80))
mapdata <-broom::tidy(worldmap)
mapdata$region <- str_replace(mapdata$region,"UK","United Kingdoms")
mapdata$region <- str_replace(mapdata$region,"USA","United States")
mapdata <- left_join(mapdata,data,by=c("region"="Country"))
# a<-aaa %>% filter(is.na(Degree)) %>% distinct(region)
mapdata$Degree[mapdata$Degree==0] <-0.1
mapdata$Degree[is.na(mapdata$Degree)] <-0.1
mapdata$Exchange[mapdata$Exchange==0] <-0.1
mapdata$Exchange[is.na(mapdata$Exchange)] <-0.1
mapdata$Language[mapdata$Language==0] <-0.1
mapdata$Language[is.na(mapdata$Language)] <-0.1

# a<-aaa %>% count(Degree)

smap <- function(data, label, field) {
  ggplot() +
    geom_polygon(data=data, aes(fill=!!sym(field), x = long, y = lat, group = group),color="grey",size=0.1) +
    theme_void() +
    scale_fill_gradient(trans="log",low="yellow",high="red",
                        breaks=c(1,100,500,1000,10000),
                        name="Number of students",
                        guide = guide_legend( keyheight = unit(3, units = "mm"),
                                              keywidth  = unit(12, units = "mm"),
                                              label.position = "bottom",
                                              title.position = 'top', nrow=1)
                        
    ) +
    geom_text_repel( data=label %>% arrange(desc(!!sym(field))) %>% head(16),
                     aes(x=longitude, y=latitude, label=paste(Country,!!sym(field))),
                     size=3) +
    labs(
      title = "Origins of international students in Taiwan",
      subtitle = paste(field,"students"),
      caption = "By Innovation Formosa. Data: National statistics, Taiwan"
    ) +
    theme(
      text = element_text(color = "#22211d"),
      plot.background = element_rect(fill = "#f5f5f2", color = NA),
      panel.background = element_rect(fill = "#f5f5f2", color = NA),
      legend.background = element_rect(fill = "#f5f5f2", color = NA),
      
      plot.title = element_text(size= 12, hjust=0.5, color = "#4e4d47"),
      plot.subtitle = element_text(size= 10, hjust=0.5, color = "#4e4d47",
                                   margin = margin(b = 0.5,  unit = "cm")),
      plot.caption = element_text( size=8, hjust=0.5, color = "#4e4d47"),
      
      legend.position = c(0.7, 0.09)
    ) +
    
    coord_map()
}
```

This analysis is based on the data published in 2020 by [National Statistics, Taiwan](https://www1.stat.gov.tw/ct.asp?xItem=15423&CtNode=4708&mp=3).

### Summary

#### Degree seeking

- Most degree seeking students are from Asian countries.
- Eswatini is the only African country sending more than 300 degree seeking students to Taiwan.

#### Chinese language

- Language course students are mainly from Asia, Europe, North, Central, and South America.
- Honduras sends the largest number of language students in Central America.

#### Exchange student

- European students come primarily to Taiwan as exchange students.
- France is ranked 1st in the number of exchange students.

### Origins of international students in Taiwan

#### Degree-seeking students in Taiwan

```{r, out.width="100%", fig.align='center',fig.cap="The number of degree-seeking students in Taiwan (By country)"}
smap(mapdata,data,"Degree")
```

```{r}
knitr::kable(row.names = T,format.args = list(big.mark = ","),
  data %>% select(Country,Degree) %>% arrange(desc(Degree)) %>% head(20)) %>%
  kable_styling(full_width = F)
```

#### Language course students in Taiwan

```{r, out.width="100%", fig.align='center',fig.cap="The number of language course students in Taiwan (By country)"}
smap(mapdata,data,"Language")
```

```{r}
knitr::kable(row.names = T,format.args = list(big.mark = ","),
  data %>% select(Country,Language) %>% arrange(desc(Language)) %>% head(20)) %>%
  kable_styling(full_width = F)
```

#### Exchange students in Taiwan

```{r, out.width="100%", fig.align='center',fig.cap="The number of exchange students in Taiwan (By country)"}
smap(mapdata,data,"Exchange")
```

```{r}
knitr::kable(row.names = T,format.args = list(big.mark = ","),
  data %>% select(Country,Exchange) %>% arrange(desc(Exchange)) %>% head(20)) %>%
  kable_styling(full_width = F)
```

### Data source

中華民國統計資訊網 Nationali Statistics, R.O.C(Taiwan)
https://www1.stat.gov.tw/ct.asp?xItem=15423&CtNode=4708&mp=3
